### 2022-09-05 latex/Chapters/DRLSearch.tex
update

\afblue

@@

\begin{python}

@@

def blind_search(initial_node, time_out):

@@

        node = pop(frontier) # pop as FIFO/LIFO for BFS/DFS

@@

\end{python}

@@

As mentioned in the abstract, \textbf{RL} (see \cite{Sutton1998} for a brilliant exposition of the basic concepts and theory) has known a bit of false start in the 1950s and 1960s but recently been extremely successfully applied to a variety of problems (from Atari to board games and puzzles, robotics and else). \textbf{RL} is concerned with how intelligent agents can learn optimal decisions from observing/experiencing rewards while interacting in their environment. One of the fundamental concept in the field is that of value function $s \to \textbf{V}(s)$, which tells us the maximum expected reward - or equivalently and better suited to our puzzle solving task, the minimum cost - the agent can obtain from a given state $s$ (if it takes optimal decisions). In finite state and transitions spaces, the value function can be remarkably computed by a rather mechanical and magic-like procedure called value-iteration (which uses the equivalent of the Bellman equation from optimal control), where each state $s$'s value is iteratively refined by combining the value of $s$'s reachable children states.
\afblue
\paragraph{}{\textbf{pseudo code -- \textbf{RL} Value Iteration}}
\begin{python}
###############################################################################
def value_iteration(states):
    """ pseudo code for RL value iteration """
    V = {state: inf for state in states}
    change = True
    while change:
        change = False
        for state, cost in V:
            V[state] = min(V[child] + t_cost for child, t_cost in state.children())
            change |= V[state] < cost
    return V 
###############################################################################
\end{python}
\black

@@

Quite similarly to \textbf{RL}, Deep Learning (\textbf{DL}) has not initially had the success the \textbf{AI} community was hoping it would. Marvin Minsky, who often took the blame for having \textit{killed} funding into the field, even regretted writing his 1969 book (\cite{minskypapert69}) in which he had proved that three-layer feed forward perceptrons were not quite the universal functions approximators some had hypothesized them to be. Since around 2006 (see \cite{GoodBengCour16} for more history of the recent burgeoning of \textbf{DL}), the field has known a rebirth, probably due to combination of factors, from ever more powerful computers and larger storage, the availability of data sets large and small on the internet, the advances in many techniques and heuristics (backward propagation, normalisation, drop-outs, different optimisation schemes, etc \dots) and the huge amount of experimentation with different architectures (from very deep feed forward fully connected networks, to convolutional, recurrent and more exoctic networks). It is not an exageration to say that \textbf{DL} has rendered obsolete entire fields of research and bodies of knowledge, most notably in \textbf{CV}, robotics, computational biology and \textbf{NLP}. \textbf{DL} has often become the method of choice to learn or approximate highly dimensional functions or random processes. The beauty of it is that the relevant features are autodiscovered during the training of the network, via back-ward propagation and trial-and-error, rather than having to be postulated or handcrafted as is often the case with other \textbf{ML} techniques.

@@

So what is the link between all of these: A$^{*}$'s heuristics, \textbf{DL}, \textbf{RL}'s value iteration?
\\
\\
Sometimes we have ways of computing good solutions/heuristics to our puzzles, but cannot computationally do this for all possible states (maybe the state space is simply too large!). One approach in that case is to compute the solution/heuristic for some states, and let a \textbf{DL} model learn how to extrapolate to the rest of the state space. This is a case of \textit{supervised} learning in some sense, since we need a teacher-solver to tell us good solutions or heuristics to extrapolate from. In very simplified pseudo code, the procedure looks like the following:
\afblue
\paragraph{}{\textbf{pseudo code -- \textbf{DL} heuristics}}
\begin{python}
###############################################################################
def deep_learning(puzzle_type,
                  teacher_heuristic,
                  loss_function,
                  network_architecture):
    """ pseudo code for learning a puzzle via deep learning and a teacher heuristic """
    target_value_function = {state: teacher_heuristic(state)
                             for state in generate_random_states(puzzle_type)}
    dl_heuristic = train_neural_network(target_value_function,
                                        loss_function,
                                        network_architecture)
    return dl_heuristic
###############################################################################
\end{python}
\black

For this project, I have implemented the above procedure of training a \textbf{DL} network from the solutions of other solvers/heuristics in a class called DeepLearner (see section \ref{sec:codelearners} for details).
\\
\\
An alternative approach in order to compute the cost-to-go is via \textbf{RL} value-iteration as described in the previous section (\ref{sec:RLTheory}) The state space is often so large however - and this certainly is the case for pretty much all \textbf{SP} and \textbf{RC}, except maybe the smallest dimensional \textbf{SP}s - that we cannot practically perform the value iteration procedure for all states. This is where \textbf{DL} comes again to the rescue to act as function approximator, combining with \textbf{RL} into what has become known as \textbf{DRL}. The subtelty is then that both the left-hand-side and right hand side in the value-iteration procedure are given by a \textbf{DL} network which we are constantly tweaking. For my implementation of \textbf{DRL}, I followed the same approach as in \cite{Mnih2013}, utilising two loops. During iteration over the first (inner) loop, the right hand-side $V$ of \ref{eq:DLVI} is computed using a fixed \textit{target-network}. The left hand side $V$ is using another \textit{current-network} which alone is modified by the \textbf{DL} learning (backward propagation and optimization), until convergence is deemed reached. When convergence in the inner loop is deemed obtained, we break out of it, and run the outer loop, which updates the \textit{target-network} via a copy of the \textit{current-network}. The outer loop is itself broken out of when deemed appropriate (some kind of convergence criteria). In simplified pseudo-code, this looks like:
\\
\\
\afblue
\paragraph{}{\textbf{pseudo code -- \textbf{DRL} heuristics}}
\begin{python}
###############################################################################
def deep_reinforcement_learning(puzzle_type,
                                loss_function,
                                max_epochs,
                                target_network_update_criteria,
                                puzzles_generation_criteria,
                                network_architecture):
    """ pseudo code for learning a puzzle via deep reinforcement learning """
    network = get_network(puzzle_type, network_architecture)
    target_network = get_network(puzzle_type, network_architecture)
    epoch = 0
    puzzles = list()
    while epoch < max_epochs and other_convergence_criteria(network):
        epoch += 1
        """ Generate a new bunch of puzzles """
        if puzzles_generation_criteria(puzzles):
            puzzles = generate_random_states(puzzle_type)
        V = dict()
        """ Compute their updated cost via value iteration ... 
             all moves are assumed to have cost 1 """
        for puzzle in puzzles:
            if puzzle.is_goal():
                V[puzzle] = 0
            else:
                V[puzzle] = min(target_network(puzzle),
                                1 + min(target_network(child) for child in puzzle.children()))
        """ Train left-hand-side network to approximate right-hand-side target network better
        i.e. perform a forward / backward-propagation update of the network
        """
        network = train_neural_network(V,
                                       loss_function,
                                       network_architecture)
        """ Update the target network if criteria are met 
        (e.g. epochs, convergence, no progress, etc...) """
        if target_network_update_criteria(network, target_network):
            target_network = copy(network)
    return network
###############################################################################
\end{python}
\black
For this project, I have implemented this procedure in a class called DeepReinforcementLearner (see section \ref{sec:codelearners} for details)

@@

Another basic concept of \textbf{RL} is that of the Q-function $Q(s, a)$, the maximum expected reward the agent can obtain from state $s$, taking action $a$ and acting optimally afterwards. Notice that the knowledge of $V$ everywhere is equivalent to that of $Q$, since obviously:
\begin{equation} \label{eq:QI}
V(s) = max_{a \in \mathcal{A}(s)} Q(s, a)
\end{equation}
where $\mathcal{A}(s)$ are the transitions/actions we can take from state $s$. Conversely, we can recover $Q$ from $V$ since:
\begin{equation} \label{eq:QI2}
Q(s, a) = R(a) + V(a(s))
\end{equation}
where $R(a)$ is the reward of performing action $a$ and $a(s)$ is the state we reach by performing action $a$ from state $s$. Similarly to the way one can compute $V$ via value-iteration (at least in finite settings), $Q$ can also be computed by iteration (See \cite{Watkins1992} for details of convergence of that procedure).
\\
\\
Similarly to our discussion about \textbf{DRL}, in cases where the state space is large, it can be useful to approximate $Q$, or a somewhat related quantity (such as e.g. a probability distribution over the actions that can be taken from $s$) by a neural network, and use a similar procedure to that of the previous section to update the right-hand-side and left-hand-side of the iterations. That becomes \textbf{DQL}!
\\
\\
I have for this project followed the exact same procedure described in \cite{https://doi.org/10.48550/arxiv.1805.07470} (and also used by alpha-go \cite{AlphaGo}): the output of the neural network that is learnt by \textbf{DQL}, which actually is surprisingly similar to the approach and pseudo code shown for \textbf{DRL} earlier. The only 3 differences are that:
\begin{itemize}
\item the networks (target and current) now output a vector of size $a$ + 1, where $a$ is the number of possible actions/moves. That is, one dimension for each of the possible actions, representing the probability/desirability of that action, and one dimension for the value-function's value.
\item the target update by Q-iteration now needs to update both the value-function and the optimal decision ($a$-dimensional vector of 0s, with a 1 for the optimal decision only)
\item the loss function used need to be compatible with the size of the output and target vectors. I have used as loss the average of the mean square error of the value function difference (current network and target) and the cross entropy loss of the actions probability versus the actual optimal move.
\item
Since in my \textbf{DRL} pseudo-code above (as well as in my actual code), the loss function is abstracted, and the network architecture (including the size of the output) configurable, the only modification to get \textbf{DQL} in lieu of \textbf{DRL} are extremely minimal, and essentially only to do with the Q-iteration-update section:

\afblue
\paragraph{}{\textbf{pseudo code -- \textbf{DQL} heuristics}}
\begin{python}
###############################################################################
def deep_q_learning(... same as DRL ...):
    """ pseudo code for learning a puzzle via deep q learning """
    # ... same as DRL ...
    nb_actions = puzzle_type.get_nb_actions()
    while epoch < max_epochs and other_convergence_criteria(network):
        # ... same as DRL ...
        Q_and_V = dict()
        """ Compute updated cost and actions via V & Q iteration ... 
             all moves are assumed to have cost 1 """
        for puzzle in puzzles:
            value = target_network(puzzle)[-1]
            actions = [0] * nb_actions
            best_action_id = 0
            if puzzle.is_goal():
                value = 0
            else:
                for action_id, child in puzzle.children():
                    child_value = target_network(child)[-1]
                    if child_value < value:
                        value = child_value
                        best_action_id = action_id
            # We update both the value function and the best action
            actions[best_action_id] = 1
            Q_and_V[puzzle] = actions + [value]
        # ... same as DRL ...
###############################################################################
\end{python}
\black

\end{itemize}
For this project, I have implemented the procedure described in \cite{https://doi.org/10.48550/arxiv.1805.07470} in a class called DeepQLearner (see section \ref{sec:codelearners} for details). The network jointly learns the value function (heuristic, or cost-to-go) as well as a probability distribution over the actions.

@@

Since my implementation of \textbf{DQL} is no longer just a cost-to-go estimate as with \textbf{DRL}, but a joint cost-to-go and distribution over actions (to be concrete, that means a 5-dimensional vector for the \textbf{SP} and a 13-dimensional vector for the \textbf{RC}). This leaves us with the question of how can we use the output of such a network to search for a solution. One simple answer (which I have tried, see e.g. subsection \ref{sec:S33DRLDQL}) is that we could disregard the distribution and only take into account the cost-to-go by simply using $A^{*}$. The rationale for doing so is that we might hope that jointly learning the cost-to-go and the actions via a combination of MSE and cross-entropy-loss leads to better heuristics, since we use more information during the learning and iterations.
\\
\\
Another possibility is to use an algorithm which combines both the actions distribution and the value function to inform its search. The Monte Carlo Tree Search (\textbf{MCTS}) is such an algorithm. In short, it generates at each step (and possibly in a distributed manner) paths to a \textit{leaf} on the frontier of unexpanded nodes, expands that node and checks if it is a goal state (and keeps going until the goal is found). The paths followed from initial state to leaves are decided via a combination of the probability distribution over actions (following the most promising actions) as well as the value function, according to a trade-off which can be tuned via a hyper-parameter. In order to prevent always following the same paths (which might take us very far from the goal), \textbf{MCTS} algorithms usually keep track of actions they have followed already and underweight their probability so that subsequent paths explore other actions.
\\
I have implemented the exact \textbf{MCTS} procedure described in \cite{https://doi.org/10.48550/arxiv.1805.07470} in a class called MonteCarloTreeSearch (see section \ref{sec:codesolvers} for details).

>>>>

\teal

@@

\begin{pseudocode}

@@

def blind_search(initial_node, time_out, search_type=Search.BFS):

@@

       # FIFO/LIFO for BFS/DFS
        node = pop_front(frontier) if search_type is Search.BFS else pop_back(frontier)

@@

\end{pseudocode}

@@

As mentioned in the abstract, \textbf{RL} (see \cite{Sutton1998} for a brilliant exposition of the basic concepts and theory) has known a bit of false start in the 1950s and 1960s but recently been extremely successfully applied to a variety of problems (from Atari to board games and puzzles, robotics and else). \textbf{RL} is concerned with how intelligent agents can learn optimal decisions from observing/experiencing rewards while interacting in their environment. One of the fundamental concept in the field is that of value function $s \to \textbf{V}(s)$, which tells us the maximum expected reward - or equivalently and better suited to our puzzle solving task, the minimum cost - the agent can obtain from a given state $s$ (if it takes optimal decisions). In finite state and transitions spaces, the value function can be remarkably computed by a rather mechanical and magic-like procedure called value-iteration (kind of the equivalent of the Bellman equation from optimal control), where each state $s$'s value is iteratively refined by combining the value of $s$'s reachable children states.
\teal
\paragraph{}{\textbf{pseudo code -- \textbf{RL} Value Iteration}}
\begin{pseudocode}
###############################################################################
def value_iteration(states):
    """ pseudo code for RL value iteration """
    V = {state: inf for state in states}
    change = True
    while change:
        change = False
        for state, cost in V:
            V[state] = min(V[child] + t_cost for child, t_cost in state.children())
            change |= V[state] < cost
    return V 
###############################################################################
\end{pseudocode}
\black

@@

Quite similarly to \textbf{RL}, Deep Learning (\textbf{DL}) has not initially had the success the \textbf{AI} community was hoping it would. Marvin Minsky, who often took the blame for having \textit{killed} funding into the field, even regretted writing his 1969 book (\cite{minskypapert69}) in which he had proved that three-layer feed forward perceptrons were not quite the universal functions approximators some had hypothesized them to be. Since around 2006 (see \cite{GoodBengCour16} for more history of the recent burgeoning of \textbf{DL}), the field has known a rebirth, probably due to a combination of factors, from ever more powerful computers and larger storage, the availability of data sets large and small on the internet, the advances in many techniques and heuristics (backward propagation, normalisation, drop-outs, different optimisation schemes, etc \dots) and the huge amount of experimentation with different architectures (from very deep feed forward fully connected networks, to convolutional, recurrent and more exoctic networks). It is not an exageration to say that \textbf{DL} has rendered obsolete entire fields of research and bodies of knowledge, most notably in \textbf{CV}, robotics, computational biology and \textbf{NLP}. \textbf{DL} has often become the method of choice to learn or approximate highly dimensional functions or random processes. The beauty of it is that the relevant features are autodiscovered during the training of the network, via back-ward propagation and trial-and-error, rather than having to be postulated or handcrafted as is often the case with other \textbf{ML} techniques.

@@

So what is the link between all of these: A$^{*}$'s heuristics, \textbf{DL}, \textbf{RL}'s value iteration?
\\
\\
Sometimes we have ways of computing good solutions/heuristics to our puzzles, but cannot computationally do this for all possible states (maybe the state space is simply too large!). One approach in that case is to compute the solution/heuristic for \textit{some manageable number of} states, and let a \textbf{DL} model learn how to extrapolate to the rest of the state space. This is a case of \textit{supervised} learning in some sense, since we need a teacher-solver to tell us good solutions or heuristics to extrapolate from. In very simplified pseudo code, the procedure looks like the following:
\teal
\paragraph{}{\textbf{pseudo code -- \textbf{DL} heuristics}}
\begin{pseudocode}
###############################################################################
def deep_learning(puzzle_type,
                  teacher_heuristic,
                  loss_function,
                  network_architecture):
    """ pseudo code for learning a puzzle via deep learning and a teacher heuristic """
    target_value_function = {state: teacher_heuristic(state)
                             for state in generate_random_states(puzzle_type)}
    dl_heuristic = train_neural_network(target_value_function,
                                        loss_function,
                                        network_architecture)
    return dl_heuristic
###############################################################################
\end{pseudocode}
\black

For this project, I have implemented the above procedure of training a \textbf{DL} network from the solutions of other solvers/heuristics in a class called DeepLearner (see section \ref{sec:codelearners} for details).
\\
\\
An alternative approach in order to compute the cost-to-go is via \textbf{RL} value-iteration as described in the previous section (\ref{sec:RLTheory}). The state space is often so large however - and this certainly is the case for pretty much all \textbf{SP} and \textbf{RC}, except maybe the smallest dimensional \textbf{SP}s - that we cannot practically perform the value iteration procedure for all states. This is where \textbf{DL} comes again to the rescue to act as function approximator, combining with \textbf{RL} into what has become known as \textbf{DRL}. The subtelty is then that both the left-hand-side and right hand side in the value-iteration procedure are given by a \textbf{DL} network which we are constantly tweaking. For my implementation of \textbf{DRL}, I followed the same approach as in \cite{Mnih2013}, utilising two loops. During iteration over the first (inner) loop, the right hand-side $V$ of the value-function update equation is computed using a fixed \textit{target-network}. The left hand side $V$ is using another \textit{current-network} which alone is modified by the \textbf{DL} learning (backward propagation and optimization), until convergence is deemed reached. When convergence in the inner loop is deemed obtained, we break out of it, and run the outer loop, which updates the \textit{target-network} via a copy of the \textit{current-network}. The outer loop is itself broken out of when deemed appropriate (some kind of convergence criteria). In simplified pseudo-code, this looks like:
\\
\\
\teal
\paragraph{}{\textbf{pseudo code -- \textbf{DRL} heuristics}}
\begin{pseudocode}
###############################################################################
def deep_reinforcement_learning(puzzle_type,
                                loss_function,
                                max_epochs,
                                target_network_update_criteria,
                                puzzles_generation_criteria,
                                network_architecture):
    """ pseudo code for learning a puzzle via deep reinforcement learning """
    net = get_network(puzzle_type, network_architecture)
    target_net = get_network(puzzle_type, network_architecture)
    epoch = 0
    puzzles = list()
    while epoch < max_epochs and other_convergence_criteria(network):
        epoch += 1
        """ Generate a new bunch of puzzles """
        if puzzles_generation_criteria(puzzles):
            puzzles = generate_random_states(puzzle_type)
        V = dict()
        """ Compute their updated cost via value iteration ... 
             all moves are assumed to have cost 1 """
        for puzzle in puzzles:
            if puzzle.is_goal():
                V[puzzle] = 0
            else:
                V[puzzle] = 1 + min(target_net(child) for child in puzzle.children()))
        """ Train lhs network to approximate rhs target network better
        i.e. perform a forward / backward-propagation update
        """
        network = train_neural_net(V,
                                   loss_function,
                                   network_architecture)
        """ Update the target network if criteria are met 
        (e.g. epochs, convergence, no progress, etc...) """
        if target_network_update_criteria(net, target_net):
            target_net = copy(net)
    return net
###############################################################################
\end{pseudocode}
\black
For this project, I have implemented the above algorithm in a class called DeepReinforcementLearner which I shall describe in details in section \ref{sec:codelearners}.

@@

Another fundamental concept of \textbf{RL} is that of the Q-function $Q(s, a)$, the maximum expected reward the agent can obtain from state $s$, taking action $a$ and acting optimally afterwards. Notice that the knowledge of $V$ everywhere is equivalent to that of $Q$, since obviously:
\begin{equation} \label{eq:QI}
V(s) = max_{a \in \mathcal{A}(s)} Q(s, a)
\end{equation}
where $\mathcal{A}(s)$ are the transitions/actions available from state $s$. Conversely, we can recover $Q$ from $V$ since:
\begin{equation} \label{eq:QI2}
Q(s, a) = R(a) + V(a(s))
\end{equation}
where $R(a)$ is the reward of performing action $a$ and $a(s)$ is the state we reach by performing action $a$ from state $s$. Similarly to the way one can compute $V$ via value-iteration (at least in finite state and action spaces), $Q$ can also be computed by iteration (See \cite{Watkins1992} for details of convergence of that procedure).
\\
\\
Similarly to our discussion about \textbf{DRL}, in cases where the state space is large, it can be useful to approximate $Q$, or a somewhat related quantity (such as e.g. a probability distribution over the actions that can be taken from $s$) by a neural network, and use a similar procedure to that of the previous section to update the right-hand-side and left-hand-side of the iterations. That becomes \textbf{DQL}!
\\
\\
I have for this project followed the exact same procedure described in \cite{https://doi.org/10.48550/arxiv.1805.07470} (and also used by alpha-go \cite{AlphaGo}): the output of the neural network that is learnt by \textbf{DQL}, which actually is surprisingly similar to the approach and pseudo code shown for \textbf{DRL} earlier. The only 3 differences are that:
\begin{itemize}
\item the networks (target and current) now output a vector of size $a$ + 1, where $a$ is the number of possible actions/moves. That is, one dimension for each of the possible actions, representing the probability/desirability of that action, and one dimension for the value-function's value.
\item the target update by Q-iteration now needs to update both the value-function and the optimal decision ($a$-dimensional vector of 0s, with a 1 for the optimal decision only)
\item the loss function used need to be compatible with the size of the output and target vectors. I have used as loss the average of the mean square error of the value function difference (current network and target) and the cross entropy loss of the actions probability versus the actual optimal move.
\end{itemize}
Since in my \textbf{DRL} pseudo-code above (as well as in my actual code), the loss function is abstracted, and the network architecture (including the size of the output) configurable, the only modification to get \textbf{DQL} in lieu of \textbf{DRL} are extremely minimal, and essentially only to do with the Q-iteration-update section:

\teal
\paragraph{}{\textbf{pseudo code -- \textbf{DQL} heuristics}}
\begin{pseudocode}
###############################################################################
def deep_q_learning(... same as DRL ...):
    """ pseudo code for learning a puzzle via deep q learning """
    # ... same as DRL ...
    nb_actions = puzzle_type.get_nb_actions()
    while epoch < max_epochs and other_convergence_criteria(network):
        # ... same as DRL ...
        Q_and_V = dict()
        """ Compute updated cost and actions via V & Q iteration ... 
             all moves are assumed to have cost 1 """
        for puzzle in puzzles:
            value = target_network(puzzle)[-1]
            actions = [0] * nb_actions
            best_action_id = 0
            if puzzle.is_goal():
                value = 0
            else:
                for action_id, child in puzzle.children():
                    child_value = target_network(child)[-1]
                    if child_value < value:
                        value = child_value
                        best_action_id = action_id
            # We update both the value function and the best action
            actions[best_action_id] = 1
            Q_and_V[puzzle] = actions + [value]
        # ... same as DRL ...
###############################################################################
\end{pseudocode}
\black

For this project, I have implemented the above algorithm in a class called DeepQLearner which I shall describe in details in section \ref{sec:codelearners}.

@@

Since my implementation of \textbf{DQL} is no longer just a cost-to-go estimate as with \textbf{DRL}, but a joint cost-to-go and distribution over actions (to be concrete, that means a 5-dimensional vector for the \textbf{SP} and a 13-dimensional vector for the \textbf{RC}). This leaves us with the question of how can we use the output of such a network to search for a solution. One simple answer (which I have tried, see e.g. subsection \ref{sec:S33DRLDQL}) is that we could disregard the distribution and only take into account the cost-to-go by simply using $A^{*}$. The rationale for doing so is that we might hope that jointly learning the cost-to-go and the actions via a combination of MSE and cross-entropy-loss produces a better network and leads to better heuristics, since we use more information during the learning and iterations.
\\
\\
Another possibility is to use an algorithm which combines both the actions distribution and the value function to inform its search. The Monte Carlo Tree Search (\textbf{MCTS}) is such an algorithm. In short, it generates at each step (and possibly in a distributed manner) paths to a \textit{leaf} on the frontier of unexpanded nodes, expands that node and checks if it is a goal state (and keeps going until the goal is found). The paths followed from initial state to leaves are decided via a combination of the probability distribution over actions (following the most promising actions) as well as the value function, according to a trade-off which can be tuned via a hyper-parameter. In order to prevent always following the same paths (which might take us very far from the goal), \textbf{MCTS} algorithms usually keep track of actions they have followed already and underweight their probability so that subsequent paths explore other actions. A pseudo code description of it looks like this:
\\
\teal
\paragraph{}{\textbf{pseudo code -- \textbf{MCTS}}}
\begin{pseudocode}
############################################################
def MCTS(initial_node, time_out, q_v_network):
    """ pseudo code for Monte Carlo Tree Search """
    initialize_time_out(time_out)
    tree = Tree(initial_node)
    while True:
        check_time_out()
        leaf = add_new_leaf(tree, q_v_network)
        if leaf.is_goal():
            return BFS(tree) # path to leaf can usually be improved by BFS
############################################################
def add_new_leaf(tree, q_v_network):
    leaf = tree.initial_node
    while leaf.expanded:
        pass
    leaf.expand() # add children of leaf to tree
    leaf.update_penalties()
    return leaf
############################################################
\end{pseudocode}
\black

I have implemented the exact \textbf{MCTS} procedure described in \cite{https://doi.org/10.48550/arxiv.1805.07470} and outlined in pseudo code above in a class called MonteCarloTreeSearch (see section \ref{sec:codesolvers} for details).
